% LaTeX resume using res.cls
\documentclass[margin]{res}
\usepackage{hyperref}
\usepackage{fancyhdr}
\setlength{\textwidth}{5.1in} % set width of text portion

\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\setlength{\headsep}{0.2in}
\rhead{Jamin.Wu07 at gmail dot com}

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Jamin Wu}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
% \moveleft.5\hoffset\centerline{Jamin.Wu07@gmail.com}
\moveleft.5\hoffset\centerline{Website: \url{https://wjmn.github.io}}
\moveleft.5\hoffset\centerline{GitHub: \url{https://github.com/wjmn}}


\begin{resume}

  \section{OBJECTIVE}
  I am interested in clinical medicine and computer science. I am particularly interested in how type systems can be used to model domain logic and how this might be applied to programs used in the medical setting.

  \section{EDUCATION}

  {\bf Bachelor of Medical Science and Doctor of Medicine} \hfill 2015-curr.\\
  {\it Monash University} \\
  Semester at Karolinska Institutet, Sweden (Exchange 2018) \\
  WAM (current): 85, InternZ Score: 5.4 \\
  \\
  {\bf Bachelor of Medical Science (Honours)} \hfill 2019\\
  {\it Monash University} --- Department of Physiology, and \\
  Department of Electrical \& Computer Systems Engineering \\
  Supervised by Dr Yan Wong \& Dr Nicholas Price \\
  Minor thesis titled {\it Generative Adversarial Networks for Simulated Prosthetic Vision} \\
  \\
  {\bf Western Australia Certificate of Education} \hfill 2010-2014 \\
  {\it Perth Modern School} \\
  ATAR: 99.95 \\

  \section{EXPERIENCE}

{\bf School of Biomedical Sciences, Monash University} \hfill 2018\\
  Summer Research Scholarship, supervised by Prof Paul McMenamin (Department of
  Anatomy and Developmental Biology).
  \begin{itemize} \itemsep -2pt
      \item Project on dissection of head and neck specimens.
      \item Applied anatomy knowledge and dissecting skills to produce
        presentable specimens.
  \end{itemize}

  {\bf School of Biomedical Sciences, Monash University} \hfill 2018\\
  Winter Research Scholarship, supervised by Dr Lan Nguyen (Department of
  Biochemistry and Molecular Biology).
  \begin{itemize} \itemsep -2pt
      \item Project on a web interface for producing survival analyses of
        open-access cancer data.
      \item Usage of Python (Flask) and JavaScript (React) to produce a web app
        hosted on a university server.
  \end{itemize}

  {\bf School of Mathematical Sciences, Monash University} \hfill 2017\\
  Summer Research Scholarship, supervised by Prof Hans de Sterck and Prof Hans
  Elmlund.
  \begin{itemize} \itemsep -2pt
      \item Project on automated particle picking for cryo-EM.
      \item Usage of Fortran for writing image processing routines within
          existing codebase.
  \end{itemize}

  {\bf School of Psychological Sciences, Monash University} \hfill 2016-2017\\
  Summer Research Scholarship, supervised by A/Prof Naotsugu Tsuchiya.
  \begin{itemize} \itemsep -2pt
    \item Project on incidental memory in rapid series visual
      presentation.
    \item Project on integrated information theory in relation to ECoG
      data.
    \item Usage of Matlab, Python and R for data analysis and
      visualisation.
\item Presentation of results and data using Jupyter Notebooks and org-babel.
  \end{itemize}

\section{AWARDS}

{\bf Grand Prize Winner} of the 2019 APL Problem Solving Competition (Dyalog)
\hfill 2019\\
{\small Received 2500 USD in recognition of solutions written in the APL programming language for a range of programming problems.}

{\bf Silver Certificate} in MUMUS Physiology Competition (MUMUS)
\hfill 2016\\
{\small 2nd place in medical student-run physiology competition.}

{\bf Year 1 Faculty Prize} (FMNHS, Monash University) \hfill 2016 \\
{\small Awarded to top two students based on Year 1 results in the MBBS cohort.}

{\bf Academic Scholarship} (Monash University) \hfill 2015-18 \\
{\small Monash Scholarship for Exceptional Achievement \hfill 2015}\\
{\small Summer Research Scholarship (School of Psychological Sciences) \hfill 2016}\\
{\small Monash Global Grant \hfill 2017}\\
{\small Summer Research Scholarship (School of Mathematical Sciences) \hfill
  2017}\\
{\small Winter Research Scholarship (School of Biomedical Sciences) \hfill 2018}\\
{\small Summer Research Scholarship (School of Biomedical Sciences) \hfill 2018}

{\bf Beazley Medal} (SCSA, Government of Western Australia) \hfill 2015 \\
{\small Awarded for highest aggregate Year 12 results in Western
  Australia.}

{\bf Cert. of Distinction} (School Curriculum and Standards Authority) \hfill 2015\\
in Mathematics, Physics, Chemistry and Japanese\\
{\small Awarded for achieving in top 0.5\% of students in course.}

{\bf Dux} (Perth Modern School) \hfill 2014\\
{\small Awarded for highest aggregate Year 12 results in school.}

{\bf Australian Chemistry Summer School} (Australian
Science Innovations) \hfill 2013\\
{\small Selection based on outstanding achievement in National
  Qualifying Exam.}

\section{SKILLS}

Experience using {\bf Python} for general programming, writing backend servers, data science and machine learning tasks on vacation-scholarship or full-year research projects. Extensive usage of numpy, scipy, matplotlib, Jupyter, flask, django, tensorflow and keras.

Experience using {\bf Matlab}, {\bf R} and {\bf Fortran} for numerical and statistical tasks during vacation projects.

Experience using {\bf JavaScript} (with React) and {\bf Elm} for frontend development, and have independently written full-stack applications consisting of a client-side single-page application and a REST backend.

Experience using {\bf APL}, {\bf J} and {\bf Haskell} for hobby programming tasks.

Well-acquainted with Git and GitHub, bash, and LaTeX.

\clearpage

\section{EXTRA-CURRICULAR}

Revision Lecturer (Treatments in Psychiatry) for Year 4 medical students \hfill 2019 \\
Revision Lecturer (Neurology) for Year 3 medical students \hfill 2018 \\
Momentum Mentor (for junior medical students) \hfill 2018-2019 \\
Volunteer software developer for Code Stroke Alert \hfill 2018 \\
Violinist in Stroket (chamber string group at Karolinska Institutet) \hfill 2018 \\
Violinist in Monash Medical Orchestra \hfill 2015-2019 \\

\section{PUBLICATIONS}

Seah, H., Burney, M., Phan, M., Shell, D., {\bf Wu, J.}, Zhou, K., Brooks, O., Coulton, B., Maingard, J., Tang, J., Yazdabadi, G., Tahayori, B., Barras, C., Kok, H., Chandra, R., Thijs, V., Brooks, D. and Asadi, H. (2019). CODE STROKE ALERT—Concept and Development of a Novel Open-Source Platform to Streamline Acute Stroke Management. {\it Frontiers in Neurology}, 10.

Matthews, J., {\bf Wu, J.}, Corneille, V., Hohwy, J., van Boxtel, J. and Tsuchiya, N. (2018). Sustained conscious access to incidental memories in RSVP. {\it Attention, Perception, & Psychophysics}, 81(1), pp.188-204. \\

\end{resume}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
